---
title: "EducatorSA Membership Data Analysis"
author: "Siwen Yang"
execute: 
  echo: false
  warning: false
  message: false
format: typst
editor: visual
---

```{r}
library(readxl)
library(tidyverse)
library(naniar)
library(visdat)
library(ggplot2)
library(knitr)
```

```{r}
wave <- read_excel("D:/Desktop/EducatorSA/WAVE_Educators SA_members_8_5_2026.xlsx")
```

```{r}
gateway <- read_excel("D:/Desktop/EducatorSA/Gateway_exports_association_users_export.xlsx")
```

# Data Cleaning and Preparation

Before the main analysis, the WAVE and Gateway membership survey data were systematically cleaned and prepared to improve data quality and ensure the reliability of the subsequent analysis. After data cleaning, 67 Gateway records and 61 WAVE records were retained for further analysis. In addition, a combined dataset containing 59 common members was created to compare selected variables between the old and new platforms.

## Data Filtering and Variable Preparation

First, records that were not relevant to the research were removed. These included Educators SA (EDSA) records, administrator accounts, and test records. Personally Identifiable Information (PII), such as names, contact details, billing information, and social media links, was also removed because it was not relevant to the research questions. This reduced the complexity of the dataset and helped protect member privacy.

Some variable names were also standardised to improve consistency and make the data easier to analyse and interpret.

```{r}
wave$`Start Date` <- as.Date(wave$`Start Date`, origin = "1899-12-30")
wave <- wave %>%
  filter(!is.na(Company))%>%
  filter(Company != "EDSA")

```

```{r}
wave <- wave %>%
  select(-c("First Name", "Last Name", "Position", "Email", "Mobile", "Address", "Suburb", "Billing Company", "Billing First name", "Billing Last name", "Billing Email", "ABN", "Package", "Duration", "Addon", "Note", "State", "Postcode", "Payment Method", "President Name", "President Email", "President Phone Number", "Vice President Name", "Vice President Email", "Vice President Phone Number", "Secretary Name", "Secretary Email", "Secretary Phone Number", "Treasurer Name", "Treasurer Email", "Treasurer Phone Number", "EdSA Representative Name", "EdSA Representative Email", "EdSA Representative Phone Number", "Website URL:", "Public facing email address:", "Phone number for public distribution (if available):", "Facebook:", "Instagram:", "Other - Please specify", "Co President Name", "Co President Email", "Co President Phone Number","LinkedIn:", "Twitter:", "Start Date", "Expiry Date","The Educators SA Association Newsletter is now our main method of communicating information to members. Are there any additional committee members who would like to be added to the distribution list? Please provide name and email addresses:")) %>%
  select(-c(ID, Type, "Tags", "Xero ID", "Membership Number")) %>%
  select(-c("What term is your current President in?", "When is your AGM due to be held?", "Does your Association have an Annual Conference?", "If so, which month?", "Do your Association ever host National Conferences?", "What are the dates of this Event/Conference?", "What is your main Event/Conference for the year?", "What are your membership renewal terms?", "If so, what year/ month is the next one scheduled to be in SA?", "If you offer any services targeted specifically at Pre-Service Educators, please specify:", "If you offer any services targeted specifically at Early Career Educators, please specify:", "If yes, please specify:", "If yes, please provide details:", "If yes, please specify"))
```

```{r}
wave <- wave %>%
  rename(number_members_2025 = `How many Members did your Association have in 2025?`, 
         acronym = `Acronym Association`, 
         number_members_2024 = `How many Members did your Association have in 2024?`, 
         number_committee_members = `How many Committee Members do you have?`, 
         asso_name = `Company`
         )
```

```{r}
# 删除测试数据
gateway <- gateway %>%
  filter(!(`Contact Name` %in% "Please")) %>%
  filter(!(Membership %in% "Admin")) %>%
  rename(acronym = `Association Acronym`, 
         asso_name = `Association Name`
         ) 
```

```{r}
gateway <- gateway %>%
  select(-c("...10", "Membership Is Subscription", "Surname", "Is Voided", "Membership Paid Date")) %>%
  select(-c("Association", "Email", "President Phone Number", "Co President Name", "Co President Email", "Co President Phone Number", "Vice President Name", "Vice President Email", "Vice President Phone Number", "Secretary Name", "Secretary Email", "Secretary Phone Number", "Treasurer Name", "Treasurer Email", "Treasurer Phone Number", "EdSA Representative Name", "EdSA Representative Email", "EdSA Representative Phone Number", "President Name", "President Email")) %>%
  select(-c(Membership, "Contact Name", "What is your main Event/Conference for the year?", "What are the dates of this Event/Conference?", "When is your AGM due to be held?", "What term is your current President in?", "What are your membership renewal terms?", "Other - Please specify", "If yes, please specify", "Would you like to be contacted regards the EdSA Gateway Membership Management system?")) %>%
  select(-c(`Signup Time`))
```

## Data Correction and Formatting

Some associations reported their membership numbers using free-text responses, such as “Approx 200” and “Around 340 members”. These responses were converted into numerical values to support further analysis. Responses where the number could not be determined, such as “Not sure” and “Can’t log in to check”, were treated as missing values.

After cleaning, relevant variables were converted to numeric format where appropriate. For variables reported as membership size or Early Career membership ranges, ordered categories were used to maintain a consistent order in cross-tabulation and visualisation. For categorical questions with missing responses, “Unsure” was used as a separate category where appropriate.

Some duplicate records were caused by system issues, where the same member had both an active and an inactive account. The newer record was retained as the main record. If some fields were missing in the newer record but valid information was available in the older record, the older information was used to supplement the newer record. Duplicate records were then removed. This approach helped retain as much useful information as possible while avoiding duplicate counting.

```{r}
#| output: false

wave[wave$number_members_2025 %in% "216 SA individual, student and institution", "number_members_2025"] <- "216"
wave[wave$number_members_2025 %in% "290 - not including school associate members (eg teachers from member schools)", "number_members_2025"] <- "290"
wave[wave$number_members_2025 %in% "Cant log in to check", "number_members_2025"] <- NA
wave[wave$number_members_2025 %in% "150 approx. we don't have a good database for 2025", "number_members_2025"] <- "150"
wave[wave$number_members_2025 %in% "43 individual, 14 schools (5 teachers per school membership) and 1 Institutional membership- Adelaide University", "number_members_2025"] <- "114"
wave[wave$number_members_2025 %in% "NA", "number_members_2025"] <- NA

wave <- wave %>%
  mutate(number_members_2025 = as.numeric(number_members_2025))
```

```{r}
#| output: false

wave[wave$number_members_2024 %in% "75 state members (national association is greater)", "number_members_2024"] <- "75"
wave[wave$number_members_2024 %in% "150ish", "number_members_2024"] <- "150"
wave[wave$number_members_2024 %in% "43 metro schools, 16 country schools, 17 individuals, 1 student", "number_members_2024"] <- "77"
wave[wave$number_members_2024 %in% "approx. 80", "number_members_2024"] <- "80"
wave[wave$number_members_2024 %in% "150ish", "number_members_2024"] <- "150"
wave[wave$number_members_2024 %in% "200 this includes organisational groups of members", "number_members_2024"] <- "200"
wave[wave$number_members_2024 %in% "170 odd", "number_members_2024"] <- "170"
wave[wave$number_members_2024 %in% "65 services", "number_members_2024"] <- "65"
wave[wave$number_members_2024 %in% "Approx 200", "number_members_2024"] <- "200"
wave[wave$number_members_2024 %in% "not sure", "number_members_2024"] <- NA
wave[wave$number_members_2024 %in% "Around 340 SA members", "number_members_2024"] <- "340"
wave[wave$number_members_2024 %in% "160 on average", "number_members_2024"] <- "160"
wave[wave$number_members_2024 %in% "check with Gateway data", "number_members_2024"] <- "50"

wave <- wave %>%
  mutate(number_members_2024 = as.numeric(number_members_2024))
wave$`How many current financial members do you have?` <- factor(wave$`How many current financial members do you have?`, levels = c("0-50", "51-100", "101-150", "151-200", "200+", "unsure"))
wave$`How many 'Early Career' or 'Pre Service' members do you have?` <- factor(wave$`How many 'Early Career' or 'Pre Service' members do you have?`, levels = c("0-10", "11-30", "31-50", "51-100", "unsure"))
```

```{r}
#| output: false

wave[wave$number_committee_members %in% "9 committee members, around 30 members", "number_committee_members"] <- "9"
wave[wave$number_committee_members %in% "Eleven", "number_committee_members"] <- "11"
wave[wave$number_committee_members %in% "Currently 6 until AGM", "number_committee_members"] <- "6"
wave[wave$number_committee_members %in% "6 general committee members", "number_committee_members"] <- "6"

wave <- wave %>%
  mutate(number_committee_members = as.numeric(number_committee_members))
```

```{r}
#| output: false

gateway$`How many current financial members do you have?`[gateway$`How many current financial members do you have?` == "100"] <- "51-100"
```

```{r}
#| output: false

# 检查重复
gateway |>
  filter(duplicated(gateway$acronym) == TRUE)

```

```{r}
#| output: false

# 删除重复
gateway <- gateway %>%
  filter(!(asso_name == "Modern Language Teachers Association of South Australia" & `Membership Number` == "EdSA1648")) %>%
  filter(!(asso_name == "The Laboratory Managers Association of SA")) %>%
  filter(!(asso_name == "Legal Education Teachers Association of South Australia")) %>%
  filter(!(asso_name == "South Australian German Teachers Association" & `Membership Number` == "EdSA1031")) %>%
  filter(!(asso_name == "History Teachers Association of South Australia" & `Membership Number` == "EdSA2737")) %>%
  filter(!(asso_name == "South Australian Council for Adult Literacy, Inc." & `Membership Number` == "EdSA2740")) %>%
  filter(!(asso_name == "Geography Teachers Association of SA" & `Membership Number` == "EdSA1073")) %>%
  filter(!(asso_name == "Geography Teacher's Assocaition of South Australia" & `Membership Number` == "EdSA4555")) %>%
  filter(!(asso_name == "Modern Greek Language Teachers Association of South Australia Inc")) %>%
  filter(!(asso_name == "The Australian Council for Educational Leaders (SA Branch)")) %>%
  filter(!(asso_name == "Out of School Hours Care (SA) Association Inc.")) 
  
  
```

```{r}
#| output: false

gateway |>
  filter(duplicated(gateway$acronym) == TRUE)
```

## Missing Data Assessment

```{r}
wave |>
  select(number_members_2024, number_members_2025) |>
  vis_miss() + 
  theme(axis.text.x = element_text(vjust = 0.2))
```

The black sections in the missing-data visualisations show where data were unavailable. For the number of members, approximately 25% of the responses were missing for 2024, while approximately 17% were missing for 2025. Many associations provided membership numbers for only one of the two years.

```{r}
gateway |>
  rename("18-25" = "If you are aware, what would be the % of your current members in each age group? Age group 18-25 in %", 
         "26-35" = "Approximately, what is the % of your current members in the age group 26-35?", 
         "36-45" = "Approximately, what is the % of your current members in the age group 36-45?", 
         "46-55" = "Approximately, what is the % of your current members in the age group 46-55?", 
         "55+" = "Approximately, what is the % of your current members in the age group 55+?") |>
  select("18-25", "26-35", "36-45", "46-55", "55+") |>
  vis_miss() + 
  theme(axis.text.x = element_text(vjust = 0.2))

```

For member age distribution, more than approximately 80% of associations on both the Gateway and WAVE platforms did not provide information about the age distribution of their members. This suggests that many associations may not have detailed information about the age structure of their membership. Due to the limited amount of valid data, age distribution was excluded from the analysis.

```{r}
wave |>
  rename("18-25" = "If you are aware, what would be the % of your current members in each age group? Age group 18-25 in %", 
         "26-35" = "Approximately, what is the % of your current members in the age group 26-35?", 
         "36-45" = "Approximately, what is the % of your current members in the age group 36-45?", 
         "46-55" = "Approximately, what is the % of your current members in the age group 46-55?", 
         "55+" = "Approximately, what is the % of your current members in the age group 55+?") |>
  select("18-25", "26-35", "36-45", "46-55", "55+") |>
  vis_miss() + 
  theme(axis.text.x = element_text(vjust = 0.2))
```

```{r}
wave <- wave |>
  select(-c("If you are aware, what would be the % of your current members in each age group? Age group 18-25 in %", "Approximately, what is the % of your current members in the age group 26-35?", "Approximately, what is the % of your current members in the age group 36-45?", "Approximately, what is the % of your current members in the age group 46-55?", "Approximately, what is the % of your current members in the age group 55+?"))
```

Other questions also had relatively high levels of missing data. Approximately 35% of responses were missing for “What is your biggest advocacy issue for 2025?” and “What are the biggest threats to your Association in 2025?”. Several other questions had missing rates of around 25%, including “What kinds of resources/publications do you provide?”, “How many current financial members do you have?”, “How many 'Early Career' or 'Pre Service' members do you have?”, “What are your membership predictions for 2025 and why?”, “What services does your Association offer?”, and “Who is your target audience?”.

The relatively high level of missing data in some questions was particularly concentrated in areas related to membership statistics, future planning, and association roles and services. This may reflect differences in how associations record information and how easily this information can be accessed. For smaller associations, missing data may not necessarily mean that the information does not exist. Instead, it may indicate that the information has not been formally recorded or is not centrally available.

In the future, Educators SA could consider providing optional data collection templates, membership management resources, or opportunities for associations to share practices. These resources could help associations improve the consistency and accessibility of their information.

```{r, eval=FALSE}
check_missing_wave <- wave |>
  select(-c(asso_name, Status, acronym, number_members_2024, number_members_2025, Industry)) |>
  miss_var_summary()

check_missing_wave
```

```{r, eval=FALSE}
check_missing_gateway <- gateway |>
  select(-c(asso_name, acronym)) |>
  miss_var_summary()

check_missing_gateway
```

## Missing Data Imputation

Membership size was an important indicator for this project, but some membership figures were missing. Approximately 25% of the 2024 membership figures and 17.2% of the 2025 figures were missing.

A step-by-step imputation approach was used to reduce information loss. If an association had a missing value for 2024 but had a valid value for 2025, the 2025 value was used to fill the missing 2024 value. Similarly, if only the 2025 value was missing, the 2024 value was used.

If membership numbers were missing for both years, the median membership number for the relevant year was used for imputation. The median was selected instead of the mean because membership size had several large outliers. Using the median therefore reduced the influence of unusually large associations on the imputed values.

```{r}
#| output: false

wave$`How many 'Early Career' or 'Pre Service' members do you have?`[is.na(wave$`How many 'Early Career' or 'Pre Service' members do you have?`)] <- "unsure"
wave$`How many current financial members do you have?`[is.na(wave$`How many current financial members do you have?`)] <- "unsure"
```

```{r}
#| output: false

glimpse(wave)
check_missing_wave <- miss_var_summary(wave)
```

```{r}
wave <- wave %>%
  mutate(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?` = ifelse(is.na(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?`), "No", `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?`))
```

```{r}
#| output: false

# 有两个association由于duplicate问题有两条数据，保留了更新的一条，有一些数据比如Industry和问卷问题，在新数据中缺失的用老数据的内容填补，来避免信息流失，其余的在检查后决定其他保持不变。
wave$Industry[wave$asso_name == "Australian Council for Educational Leaders"] <- "Education and Training"

wave <- wave %>%
  filter( asso_name != "Australian Council of Educational Leaders (SA Branch)")
```

```{r}
#| output: false

wave$Industry[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "Education and Training"
wave$`What services does your Association offer?`[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "Professional learning; Publications; Advocacy; Student/Learner Activities"
wave$`Who is your target audience?`[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "Home Economics/ Technology teachers"
wave$`What kinds of resources/publications do you provide?`[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "National journal and newsletter"
wave$`What is your biggest advocacy issue for 2025?`[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "Where does Home ec fit in the curriculum?"
wave$`What are the biggest threats to your Association in 2025?`[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "Finances and keeping our association alive in SA!"
wave$number_members_2024[wave$asso_name == "Home Economics Institute of Australia Inc"] <- 600
wave$`What are your membership predictions for 2025 and why?`[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "We'd like to grow our school membership by 5"
wave$`How many 'Early Career' or 'Pre Service' members do you have?`[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "11-30"
wave$`How many current financial members do you have?`[wave$asso_name == "Home Economics Institute of Australia Inc"] <- "200+"

# 注意这里Australian Council for Health, Physical Education & Recreation (SA Branch)没有任何信息，被删除。
wave <- wave %>%
  filter( asso_name != "Home Economics Institute of Australia (SA)") %>%
  filter( asso_name != "Australian Council for Health, Physical Education & Recreation (SA Branch)")
```

```{r}
# 用中位数填补缺失值来避免极端值影响结果
# 注意，由于在2024有25%的members没有填写人数，在2025有17.2%的人没有填写，有一年数据缺失的用另一年数据填补，两年都缺失的，用中位数填补，尽可能使数据准确

wave_filled <- wave %>%
  mutate(number_members_2025 = ifelse(is.na(number_members_2025), number_members_2024, number_members_2025)) %>%
  mutate(number_members_2024 = ifelse(is.na(number_members_2024), number_members_2025, number_members_2024)) %>%
  mutate(number_members_2024 = ifelse(is.na(number_members_2024), 79, number_members_2024), 
         number_members_2025 = ifelse(is.na(number_members_2025), 85, number_members_2025)) 

```

## Manual Data Validation and Platform Comparison

Some association names were entered slightly differently in the Gateway and WAVE platforms. These differences prevented records belonging to the same association from being correctly matched when the datasets were merged. The association names were therefore manually checked and standardised across the two datasets.

```{r}
#| output: false

# 统一名字
gateway$asso_name[gateway$asso_name == "Association of Heads of Music in Non-Government Schools South Australia Inc."] <- "Association of Heads of Music in Non Government Schools South Australia Inc."
gateway$asso_name[gateway$asso_name == "Australian Association of Special Education"] <- "Australian Association of Special Education (SA Chapter)"
gateway$asso_name[gateway$asso_name == "Australian Association of Teachers of the Deaf (SA) Inc."] <- "Australian Association of Teachers of the Deaf (SA Branch)"
gateway$asso_name[gateway$asso_name == "AUSTRALIAN NATIONAL CHORAL ASSOCIATION (ANCA) INCORPORATED trading as ANCA South Australia"] <- "Australian National Choral Association (SA Chapter)"
gateway$asso_name[gateway$asso_name == "The Chinese Language Teachers Association SA (CLTASA)"] <- "The Chinese Language Teachers Association of South Australia Inc."
gateway$asso_name[gateway$asso_name == "HaSS Association Australia"] <- "HaSS Association Australia (HAA)"
gateway$asso_name[gateway$asso_name == "History Teachers Association of South Australia"] <- "History Teachers' Association of SA"
gateway$asso_name[gateway$asso_name == "Indonesian Teachers' Association"] <- "Indonesian Teachers' Association Inc."
gateway$asso_name[gateway$asso_name == "Japanese Language Teachers' Association of South Australia Incorporated"] <- "Japanese Language Teachers' Association of South Australia"
gateway$asso_name[gateway$asso_name == "Kodaly Music Education Institute of Australia"] <- "Kodaly Music Education Institute of Australian, SA Branch"
gateway$asso_name[gateway$asso_name == "The Chinese Language Teachers Association SA (CLTASA)"] <- "The Chinese Language Teachers Association of South Australia Inc."
gateway$asso_name[gateway$asso_name == "Australian Association of Special Education"] <- "Australian Association of Special Education (SA Chapter)"
gateway$asso_name[gateway$asso_name == "OSHC SA"] <- "Out of Hours School Care SA"
wave$asso_name[wave$asso_name == "Language Teachers SA - MLTASA"] <- "Modern Language Teachers Association of South Australia"
gateway$asso_name[gateway$asso_name == "Home Economics Institute of Australia- South Australian Division"] <- "Home Economics Institute of Australia Inc"
gateway$asso_name[gateway$asso_name == "AUSTRALIAN DANCE COUNCIL AUSDANCE SA INC"] <- "Ausdance SA - Australian Dance Council"
gateway$asso_name[gateway$asso_name == "Australian Council of Educational Leaders (SA Branch)"] <- "Australian Council for Educational Leaders"
gateway$asso_name[gateway$asso_name == "Spanish Teachers' Association of South Australia"] <- "Spanish Teachers' Association of SA"
gateway$asso_name[gateway$asso_name == "Australian Band and Orchestra Directors Association (South Australia)"] <- "Australian Band and Orchestra Directors Association"
gateway$asso_name[gateway$asso_name == "Australian Psychologists and Counsellors in Schools SA"] <- "Australian Psychologists and Counsellors in Schools Association - South Australia"
wave$asso_name[wave$asso_name == "SA HALT Network"] <- "SA Highly Accomplished Lead Teachers Network"
wave$acronym[wave$asso_name == "SA Highly Accomplished Lead Teachers Network"] <- "SA HALT Network"
gateway$asso_name[gateway$asso_name == "South Australian association for Teaching English to Speakers of Other Languages Inc"] <- "South Australian Association for Teaching English to Speakers of Other Languages Inc"
gateway$asso_name[gateway$asso_name == "SA Special Education Principals & Leaders Association"] <- "South Australian Special Education Principals and Leaders Association"
gateway$asso_name[gateway$asso_name == "Outdoor Education Association of South Australia"] <- "Outdoor Educators' Association of South Australia"
gateway$asso_name[gateway$asso_name == "Orff Schulwerk Association of SA Inc"] <- "Orff Schulwerk Association of SA"
gateway$asso_name[gateway$asso_name == "The Laboratory Managers Association of SA. Inc"] <- "Laboratory Managers Association of South Australia"
gateway$asso_name[gateway$asso_name == "Geography Teachers Association of South Australia"] <- "Geography Teachers Association of SA"
gateway$asso_name[gateway$asso_name == "BETA SA Inc"] <- "Business and Enterprise Teachers Association of South Australia"
gateway$asso_name[gateway$asso_name == "Australia Society for Music Education SA Chapter"] <- "Australian Society for Music Education SA Chapter"
gateway$asso_name[gateway$asso_name == "Early Childhood Australia: South Australia Committee"] <- "Early Childhood Australia SA Branch"
gateway$asso_name[gateway$asso_name == "Early Childhood Association"] <- "Early Childhood Organisation"
gateway$asso_name[gateway$asso_name == "Early Childhood Australia: South Australia Committee"] <- "Early Childhood Australia SA Branch"


gateway$asso_name[gateway$asso_name == "Early Childhood Association"] <- "Early Childhood Organisation"
```

```{r}
#| output: false

new_member <- anti_join(wave, gateway, by = "asso_name")
leave_member <- anti_join(gateway, wave, by = "asso_name")
common_member <- inner_join(gateway, wave, by = "asso_name", suffix = c("_gateway", "_wave"))
```

New members:

```{r}
new_member |>
  select(asso_name) |>
  rename(`Association Name` = asso_name) |>
  kable()
```

Leave members:

```{r}
leave_member |>
  select(asso_name) |>
  rename(`Association Name` = asso_name) |>
  kable()
```

A comparison of the old and new platform data identified four new associations that joined Educators SA. There were also eight associations with no data recorded in the WAVE platform. ACHPER (SA) remains an active member but had not registered on the new platform, while the other seven associations can be considered associations that have left Educators SA.

Overall, the WAVE survey contains more comprehensive questions than the Gateway survey, but it also has a higher level of missing data in several areas. This may partly be related to the fact that WAVE is a newer platform and associations may still be adapting to the new system.

# Membership Size and Trends

## Current Financial Membership

```{r}
wave |>
  filter(!is.na(`How many current financial members do you have?`)) |>
  ggplot(aes(x = `How many current financial members do you have?`)) +
  geom_bar() + 
  coord_cartesian(ylim = c(0,30))

```

The bar chart shows that most associations have fewer than 100 financial members, while approximately ten associations have more than 200 financial members. According to the data, more than half of the members in most associations are financial members.

There are also two potential outliers in the dataset. These associations reported fewer than 100 total members in 2025 but selected “200+” for their number of financial members. This may indicate data entry errors and should be checked with the relevant associations if the data are used for further analysis.

```{r}
gateway |>
  filter(!is.na(`How many current financial members do you have?`)) |>
  mutate(`How many current financial members do you have?` = factor(`How many current financial members do you have?`, levels = c("0-50", "51-100", "101-150", "151-200", "200+"))) |>
  ggplot(aes(x = `How many current financial members do you have?`)) +
  geom_bar() + 
  coord_cartesian(ylim = c(0,30))

```

The comparison between Gateway and WAVE shows that the proportion of associations in the “0–50” category has decreased, while the overall distribution remains relatively similar. However, 14 associations on the WAVE platform did not provide information for this question. Therefore, the frequencies between the two platforms should not be directly compared without considering the missing responses.

```{r}
# 一起的
# How many 'Early Career' or 'Pre Service' members do you have?
compare_financial_memb <- bind_rows(
  common_member %>%
    select(`How many current financial members do you have?_gateway`) %>%
    mutate( Platform = "Gateway", 
            `How many current financial members do you have?` = `How many current financial members do you have?_gateway`),

  common_member %>%
    select(`How many current financial members do you have?_wave`) %>%
    mutate( Platform = "WAVE", 
            `How many current financial members do you have?` = `How many current financial members do you have?_wave`)
  
) %>%
  count(`How many current financial members do you have?`, Platform)

compare_financial_memb %>%
#  mutate(`How many current financial members do you have?` = fct_relevel(`How many current financial members do you have?`, "Unsure", after = Inf)) %>%
  mutate(`How many current financial members do you have?` = factor(`How many current financial members do you have?`, levels = c("0-50", "51-100", "101-150", "151-200",  "200+", "unsure"))) %>%
  ggplot(aes(x = `How many current financial members do you have?`, y = n, fill = Platform)) +
  geom_col(position = "dodge") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(y = "Count",title = "Current Financial Member Distribution Across Gateway and WAVE Platforms")
```

This chart shows the distribution of current financial members among associations that are present on both the Gateway and WAVE platforms. Membership size was divided into six categories: 0–50, 51–100, 101–150, 151–200, and 200+ members.

Overall, associations on both platforms are mainly concentrated in the smaller membership categories. The 0–50 and 51–100 categories are the most common. On Gateway, approximately 21 and 19 associations fall into these two categories respectively, while WAVE has 16 associations in each category. In comparison, fewer associations have between 101 and 150 members, with approximately six associations on each platform.

For larger associations, only one association on each platform has between 151 and 200 members. The 200+ category also represents a relatively large group, with 12 associations on Gateway and 10 on WAVE. This indicates that some associations have relatively large and established membership bases.

In addition, approximately 10 associations on WAVE did not provide an answer to this question, while there were very few such records on Gateway. This may partly reflect the fact that WAVE is a newer platform and some association information has not yet been fully recorded.

Overall, the distribution remains relatively consistent between the two platforms, as there has not been a major change in membership size among associations that appear on both platforms. The number of associations in the 0–100 and 200+ categories is slightly higher on Gateway than on WAVE, which may partly be due to incomplete information on the WAVE platform.

Across both platforms, the majority of associations have no more than 100 financial members, indicating that Educators SA's member associations are generally small organisations. At the same time, the 200+ category also contains a relatively large number of associations, while the number of associations in the 101–200 range is much smaller. This suggests that association size may show some degree of polarisation, with many smaller associations and another group with a relatively large membership base.

The relatively high number of “Unsure” responses on the WAVE platform also indicates some uncertainty around membership size data. Improving the accuracy and completeness of membership records should therefore be considered a priority.

## Changes in Membership Size from 2024 to 2025

```{r}
#| output: false

mean(wave$number_members_2024, na.rm = TRUE)
median(wave$number_members_2024, na.rm = TRUE)
```

```{r}
#| output: false

mean(wave$number_members_2025, na.rm = TRUE)
median(wave$number_members_2025, na.rm = TRUE)
```

The average membership size was approximately 135 in 2024, with a median of 77. In 2025, the average increased to approximately 321, while the median increased to 85. Compared with 2024, the average membership size more than doubled, while the median increased from 77 to 85. This suggests an overall increase in membership across associations.

```{r}
wave_filled |>
  ggplot(aes(x = number_members_2024, y = number_members_2025)) + 
  geom_point() + 
  geom_text(aes(label = acronym), hjust = -0.2, size = 3)
```

The Primary English Teaching Association Australia (PETAA) had 5,200 members in 2025, considerably higher than other associations and accounting for approximately 28% of the estimated total membership. However, PETAA reported only 200 members in 2024, representing a very large increase within one year. This was confirmed to be related to a partnership with government departments, through which a large number of people were automatically registered as members.

The Australian Council for Educational Leaders (ACEL) had approximately 4,000 members, accounting for around 21% of the total. The South Australian Science Teachers Association (SASTA) had more than 1,700 members, making it the third-largest association by membership size. Compared with 2024, SASTA's membership increased slightly and remained relatively stable overall.

## Membership Growth Expectations

```{r}
wave |>
  ggplot(aes(x = `Was that an increase, decrease or stable number?`)) + 
  geom_bar()
```

Most associations reported relatively stable membership numbers. Twelve associations indicated that their membership was increasing, while 10 reported a decline.

It is worth noting that the Australian Council for Educational Leaders (ACEL), which had approximately 4,000 members in 2025, also reported a decline in membership. This suggests that a large membership base does not necessarily mean that an association is experiencing membership growth.

## Early Career and Pre-Service Membership

```{r}
# How many 'Early Career' or 'Pre Service' members do you have?
compare_early_career <- bind_rows(
  gateway %>%
    select(`How many 'Early Career' or 'Pre Service' members do you have?`) %>%
    mutate( Platform = "Gateway"),

  wave %>%
    select(`How many 'Early Career' or 'Pre Service' members do you have?`) %>%
    mutate( Platform = "WAVE")
  
) %>%
  count(`How many 'Early Career' or 'Pre Service' members do you have?`, Platform)

compare_early_career %>%
  mutate(`How many 'Early Career' or 'Pre Service' members do you have?` = fct_relevel(`How many 'Early Career' or 'Pre Service' members do you have?`, "Unsure", after = Inf)) %>%
  mutate(`How many 'Early Career' or 'Pre Service' members do you have?` = factor(`How many 'Early Career' or 'Pre Service' members do you have?`, levels = c("0-10", "11-30", "31-50", "51-100", "100+", "unsure"))) %>%
  ggplot(aes(x = `How many 'Early Career' or 'Pre Service' members do you have?`, y = n, fill = Platform)) +
  geom_col(position = "dodge") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(y = "Count",title = "Distribution of Early Career/Pre-Service Members Across Gateway and WAVE platforms")
```

The chart shows the distribution of Early Career and Pre-Service members across associations on the Gateway and WAVE platforms.

Overall, most associations have a relatively small number of Early Career or Pre-Service members. On both platforms, the 0–10 category accounts for the largest group, with 46 associations on Gateway and 32 on WAVE. This is considerably higher than the other membership categories. Very few associations have more than 30 Early Career or Pre-Service members.

There are also 18 associations on WAVE that did not provide information about their Early Career or Pre-Service membership, compared with nine on Gateway. This suggests that some associations may not have accurate or complete records of their Early Career and Pre-Service members.

Across both Gateway and WAVE, most associations have no more than 10 Early Career or Pre-Service members. This indicates that Early Career and Pre-Service members represent a relatively small group within the membership structure of many associations and may not yet be a major part of their overall membership.

Although relatively uncommon, some associations have between 31–50 or 51–100 Early Career or Pre-Service members. This suggests that some associations have developed stronger participation among these groups. The approaches used by these associations may be useful for further investigation and sharing of practices.

The WAVE platform has approximately one-third of associations unable to provide a clear number of Early Career or Pre-Service members, with 18 associations recorded as “Unsure”. This is higher than on Gateway. This may affect the accuracy of future assessments of participation among Early Career and Pre-Service members and highlights the need for stronger membership classification and record-keeping practices.

## Membership Discounts for Early Career and Pre-Service Educators

```{r}
compare_early_career_discount <- bind_rows(
  common_member %>%
    select(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_gateway`) %>%
    mutate( Platform = "Gateway", 
            `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?` = `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_gateway`),

  common_member %>%
    select(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_wave`) %>%
    mutate( Platform = "WAVE", 
            `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?` = `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_wave`)
  
) %>%
  count(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?`, Platform)

compare_early_career_discount %>%
  mutate(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?` = factor(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?`, levels = c("Yes", "No"))) %>%
  ggplot(aes(x = `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?`, y = n, fill = Platform)) +
  geom_col(position = "dodge") +
  theme_minimal() +
  labs(y = "Count",title = "")
```

The data show that a large majority of associations, approximately 71.9%, offer discounted membership to Early Career or Pre-Service educators.

When comparing Gateway and WAVE, the number of associations offering discounted membership increased from 45 to approximately 60, while the number of associations that do not offer a discount decreased slightly.

```{r}
#| output: false

gateway_tab <- table(
  common_member$`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_gateway`, 
  common_member$`How many 'Early Career' or 'Pre Service' members do you have?_gateway`
)
```

```{r, eval=FALSE}
#| output: false

prop.table(gateway_tab)
```

```{r, eval=FALSE}
#| output: false

wave_tab <- table(
  common_member$`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_wave`, 
  common_member$`How many 'Early Career' or 'Pre Service' members do you have?_wave`
)

```

```{r, eval=FALSE}
#| output: false

common_member %>%
  filter(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_gateway` == "No" & `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_wave` == "Yes") %>%
  select(asso_name, `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_gateway`, `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_wave`, `How many 'Early Career' or 'Pre Service' members do you have?_gateway`, `How many 'Early Career' or 'Pre Service' members do you have?_wave`)
```

```{r, eval=FALSE}
#| output: false

common_member %>%
  filter(`Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_gateway` == "Yes" & `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_wave` == "No") %>%
  select(asso_name, `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_gateway`, `Do you offer a discounted membership to "Early Careers" or "Pre-Service"?_wave`, `How many 'Early Career' or 'Pre Service' members do you have?_gateway`, `How many 'Early Career' or 'Pre Service' members do you have?_wave`)
```

Among the 33 associations that appear in both datasets, three associations changed from not offering a discount to offering one. Two associations changed in the opposite direction, moving from offering a discount to no longer offering a discount.

## Services for Early Career and Pre-Service Educators

```{r, eval=FALSE}
# LLM

LLM_wave_pre <- wave %>%
  mutate(serial_num = row_number()) %>%
  select("serial_num", "Do you offer any services targeted specifically at Pre-Service educators?", "Do you offer any services targeted specifically at Early Career Educators?")

write.csv(LLM_wave_pre, "data/LLM_wave_pre.csv")
```

```{r}
LLM_wave_pre_classified <- read_csv("data/LLM_wave_pre_classified.csv") %>%
  select(-"Unnamed: 0")
```

```{r}
pre_data <- LLM_wave_pre_classified |>
  separate_rows(`Pre-Service Educator Service Categories`, sep = ";") %>%
  filter(`Pre-Service Educator Service Categories` != "No service reported") %>%
  select(Category = `Pre-Service Educator Service Categories`) %>%
  mutate(Group = "Pre-Service")

early_data <- LLM_wave_pre_classified |>
  separate_rows(`Early Career Educator Service Categories`, sep = ";") %>%
  filter(`Early Career Educator Service Categories` != "No service reported") %>%
  select(Category = `Early Career Educator Service Categories`) %>%
  mutate(Group = "Early Career")

bind_rows(pre_data, early_data) %>%
  count(Group, Category, sort = TRUE) %>%
  group_by(Group) %>%
  mutate(Category = fct_relevel(Category, "Other/Unclear", after = Inf)) %>%
  ggplot(aes(x = Category, y = n, fill = Group)) + 
  geom_col(position = "dodge") + 
  labs(title = "Comparison of Service Offerings Between Pre-Service and Early Career Educators", x = "Service Categories", y = "Count") + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

The services offered to Early Career and Pre-Service Educators show several common themes. More than 10 associations in both groups mentioned Professional Development and Training. This suggests that when associations provide specific services for these groups, they commonly focus on training, professional development, and improving professional skills.

Events and Conferences were also relatively consistent and were frequently mentioned as a benefit for both groups. Conferences and events may provide an important way for associations to connect with Pre-Service and Early Career Educators and provide opportunities for professional learning.

A notable difference is that Membership and Fee Support was mentioned more frequently for Pre-Service Educators. This may indicate that associations are more likely to use discounted membership fees and membership support to encourage or support Pre-Service Educators to join professional associations. For Pre-Service Educators, reducing the cost of membership may therefore be an important form of support.

In contrast, Networking and Community Support was more prominent among Early Career Educators. This may reflect the different needs of educators who have already entered the profession, including opportunities to build professional networks, connect with peers, and participate in professional communities.

Some associations also mentioned Mentoring, although this was less common. This suggests that mentoring is currently not one of the most widely offered services across associations. Other forms of support mentioned included Career and Employment Support and Classroom and Practical Support.

The “Other/Unclear” category mainly includes organisations that answered “Yes” but did not provide further details about the specific service offered.

```{r}
#| output: false

wave |>
  filter(`How many 'Early Career' or 'Pre Service' members do you have?` == "51-100")
```

# Events and Activities

## Event Types

```{r, eval=FALSE}
# LLM

LLM_wave_eve <- wave %>%
  mutate(serial_num = row_number()) %>%
  select("How many professional learning events does your Association run each year?", "What type of events are they?", "What locations are you using to run your events?", "Who are your target Members?", "What are your Member categories?", "How do you advertise for Members?")

write.csv(LLM_wave_eve, "data/LLM_wave_eve.csv")
```

```{r}
LLM_wave_eve_classified <- read_csv("data/LLM_wave_eve_classified.csv")
```

```{r}
LLM_wave_eve_classified$`Classification - Professional Learning Event Frequency`[LLM_wave_eve_classified$`How many professional learning events does your Association run each year?` == "4 in late 2024 and panning for 10 in 2025"] <- "2-5"

LLM_wave_eve_classified$`Classification - Professional Learning Event Frequency`[LLM_wave_eve_classified$`How many professional learning events does your Association run each year?` == "2"] <- "2-5"

LLM_wave_eve_classified$`Classification - Professional Learning Event Frequency`[LLM_wave_eve_classified$`How many professional learning events does your Association run each year?` == "up to 8"] <- "5-10"
```

```{r}
LLM_wave_eve_classified |>
  separate_rows(`Classification - Event Types`, sep = "; ") %>%
  filter(`Classification - Event Types` != "Unsure") %>%
  mutate(`Classification - Event Types` = fct_relevel(`Classification - Event Types`, "Other", after = Inf)) %>%
  ggplot(aes(x = `Classification - Event Types`)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Distribution of Event Types by Classification", x = "Event Types", y = "Count")

```

The most commonly organised event types are Professional Learning / Workshops and Conferences. Online / Hybrid Events account for a relatively small proportion, at approximately 11%. In addition to regular professional learning activities, some associations also organise Networking / Community Events and Competitions.

This suggests that most associations organise events not only to improve teaching knowledge and professional skills, but also to provide opportunities for members to communicate, connect, and learn from each other.

## Event Locations

```{r}
LLM_wave_eve_classified |>
  separate_rows(`Classification - Event Locations`, sep = "; ") %>%
  filter(`Classification - Event Locations` != "Unsure") %>%
  mutate(`Classification - Event Locations` = fct_relevel(`Classification - Event Locations`, "Other", after = Inf)) %>%
  ggplot(aes(x = `Classification - Event Locations`)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Distribution of Event Locations by Classification", x = "Event Locations", y = "Count")

```

The bar chart shows the frequency with which different event locations were mentioned. Schools are clearly the most commonly used location, with more than 30 mentions. Universities, as higher education institutions, were mentioned nine times. Other education-related or public locations, such as Community venues (15 mentions) and Training Centres (17 mentions), were also commonly used.

Nine associations reported using Conference Venues, such as hotels, for their events. Online events were also mentioned nine times. Only one association reported using its own dedicated facilities to host events.

Overall, associations use a relatively wide range of locations for their events. Schools and universities are the most common choices, followed by Training Centres, Community venues, and Conference Venues such as hotels. Some associations also organise online events, but these remain relatively uncommon, accounting for approximately 11% of the mentions. Only a very small number of associations have dedicated facilities for hosting events.

## Event Type Diversity

```{r}
event_diversity <- LLM_wave_eve_classified |>
  mutate(
    n_event_types =
      str_count(`Classification - Event Types`, ";") + 1
  )

ggplot(event_diversity,
       aes(x = n_event_types)) +
  geom_bar() + 
  labs(title = "Number of Event Types per Association", x="Number of Event Types", y="Count of Associations")
```

More than half of the associations, approximately 27, organise only one type of event. This may indicate that many associations have a relatively focused event offering or have limited resources and capacity to provide a wider range of activities. However, it is also possible that some associations only reported the event type they use most frequently in the survey.

Approximately 12 associations organise two types of events, compared with around 18 associations that organise three types. This indicates that a relatively large proportion of associations offer a wider range of activities. However, fewer than five associations organise four types of events, accounting for only 6.6% of the sample. This suggests that highly diverse event offerings are relatively uncommon and may be affected by limitations in staffing, funding, or professional capacity.

```{r}
event_type_by_diversity <- LLM_wave_eve_classified |>
  mutate(
    n_event_types =
      str_count(`Classification - Event Types`, ";") + 1
  ) |>
  separate_rows(`Classification - Event Types`, sep = "; ") |>
  filter(`Classification - Event Types` != "Unsure") |>
  count(
    n_event_types,
    `Classification - Event Types`
  ) |>
  group_by(n_event_types) |>
  mutate(
    pct = n / sum(n) * 100
  )

ggplot(event_type_by_diversity,aes(x = factor(n_event_types),y = pct,fill = `Classification - Event Types`)) +
  geom_col() +
  labs(x = "Number of Event Types", y = "Percentage", fill = "Event Types")

```

The following chart shows the proportion of different event types organised by associations with different levels of event diversity. Across all levels of diversity, Professional Learning Events remain the main type of activity. This is particularly clear among associations offering only one or two event types, where Professional Learning Events account for more than 70% of their activities.

As the number of event types increases, Community Events gradually become a more important part of the overall event mix. Their share increases from approximately 3% to around 20%. This may suggest that when associations have greater capacity to expand their event offerings, they may also introduce more social and community-based activities to strengthen connections between members.

When event diversity increases from two to three or four types, Presentations / Seminars and Online / Hybrid Events also show a clear increase and become more important parts of the event mix. Special Events, such as Competitions, also increase slightly, although they remain the least common event type.

Overall, as event offerings become more diverse, the distribution across different event types becomes more balanced. Among associations with more diverse event programs, some expand beyond basic professional learning and conference activities by adding Presentations / Seminars to provide more specialised content, while others introduce Online / Hybrid Events to overcome the limitations of face-to-face activities and reach more members.

## Event Frequency and Diversity

```{r}
event_type_by_frequency <- LLM_wave_eve_classified |>
  separate_rows(`Classification - Event Types`, sep = "; ") |>
  filter(`Classification - Event Types` != "Unsure") |>
  filter(`Classification - Event Types` != "Other") |>
  count(
    `Classification - Professional Learning Event Frequency`,
    `Classification - Event Types`
  ) |>
  group_by(`Classification - Professional Learning Event Frequency`) |>
  mutate(
    pct = n / sum(n) * 100
  ) |>
  ungroup() |>
  mutate(`Classification - Professional Learning Event Frequency` = factor(`Classification - Professional Learning Event Frequency`, levels = c("1", "2-5", "5-10", "10-20", ">20", "Other"))) |>
  filter(!(`Classification - Professional Learning Event Frequency` == "Other")) 

ggplot(event_type_by_frequency,aes(x = `Classification - Professional Learning Event Frequency`, y = `Classification - Event Types`, fill = pct)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(n, "\n(", round(pct, 1), "%)")),
    size = 3) +
  scale_fill_gradient(low = "white", high = "steelblue") +
  labs(x = "Professional Learning Event Frequency", y = "Event Type", fill = "% within\nFrequency Group") +
  theme_minimal()
```

According to the heatmap, event frequency is relatively concentrated. Most associations organise between 2 and 5 events per year, accounting for approximately 72% of the sample. The proportion of associations gradually decreases as the number of events increases, with only three associations, approximately 5%, organising more than 20 events per year.

This indicates that most associations organise no more than five events each year, while a small number of associations have a much higher level of event activity.

The heatmap also shows the relationship between event frequency and event type. Overall, regardless of how many events an association organises each year, Professional Learning and Conferences remain the core event types, consistent with the earlier findings.

Among associations organising 2–5 events per year, which is the largest group, Professional Learning / Workshops account for 39.7% and Conferences account for 26.0%. Together, these two categories represent more than 60% of the events. This shows that professional learning and conferences remain the main forms of activity. Networking / Community Events also account for 16.4%, indicating that some associations place importance on member communication and connections in addition to professional development.

Among associations organising 5–10 events per year, the event structure is more balanced. In addition to Professional Learning / Workshops (17.4%) and Conferences (21.7%), Online / Hybrid Events (26.1%) and Presentations / Seminars (21.7%) account for similar proportions. This suggests that some associations with more frequent activities also use a wider range of event formats rather than relying mainly on traditional workshops and conferences.

The relatively high proportion of Online / Hybrid Events among associations with higher event frequency may suggest that online activities are more commonly used by associations with greater organisational capacity or more frequent event programs. For associations organising fewer events, face-to-face activities remain more common. This may indicate that some associations still face challenges related to technology, staffing, or experience in organising online activities.

Across both event diversity and event frequency, Networking / Community Events are an important part of association activities. In particular, Community Events become more prominent as the scale of activities or the number of event types increases. This suggests that after meeting members' basic professional learning needs, associations may place greater emphasis on communication, collaboration, community building, and professional networking.

In other words, the development of association activities may move from knowledge sharing towards broader community connection as the range and scale of activities increase.

Overall, most associations are able to provide regular professional learning activities, but their event offerings remain relatively concentrated. Associations with higher event frequency and greater event diversity show a broader range of activities, including online events, specialised presentations, and community activities.

Educators SA could consider using its platform and resources to help associations explore different event formats. For example, an event practice-sharing mechanism could allow associations with more experience to share approaches to online event organisation, community event management, and diverse event design. Educators SA could also provide access to venues, event planning templates, or opportunities for joint events to reduce the cost and effort for smaller associations when trying new event formats.

These approaches could help increase the diversity of association activities while also supporting member participation and collaboration across associations.

# Member Recruitment and Communication

## Target Members

```{r}
LLM_wave_eve_classified |>
  separate_rows(`Classification - Target Members`, sep = "; ") %>%
  mutate(`Classification - Target Members` = fct_relevel(`Classification - Target Members`, "Other", after = Inf)) %>%
  ggplot(aes(x = `Classification - Target Members`)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Among the 61 associations, more than 50 identified Educators and Professional Practitioners as their target members, accounting for approximately 82% of the sample. This was the most commonly identified target group. Other frequently mentioned target groups included Leaders / Senior Professionals and Students / Pre-Service / Early Career members.

Approximately 20% of associations also identified Schools / Organisations / Services as target audiences.

## Membership Categories

```{r}
LLM_wave_eve_classified |>
  separate_rows(`Classification - Member Categories`, sep = "; ") %>%
  mutate(`Classification - Member Categories` = fct_relevel(`Classification - Member Categories`, "Other", after = Inf)) %>%
  ggplot(aes(x = `Classification - Member Categories`)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

More than 40 associations offer not only Individual / Full Membership but also membership types for organisations, such as schools. Membership categories for Students and Pre-Service members were also common.

It is worth noting that many associations provide specific membership categories for Students and Pre-Service members, which is much more common than providing a specific category for Early Career members. Around 20 associations also offer Retired / Life / Honorary Membership.

Overall, membership categories are mainly differentiated by the type of member, such as individuals or organisations, and by members' career stage.

## Member Advertising and Recruitment Channels

```{r}
LLM_wave_eve_classified |>
  separate_rows(`Classification - Member Advertising`, sep = "; ") %>%
  mutate(`Classification - Member Advertising` = fct_relevel(`Classification - Member Advertising`, "Other", after = Inf)) %>%
  ggplot(aes(x = `Classification - Member Advertising`)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

For member recruitment, Email / Direct Mail / Newsletter and Social Media / Digital Platforms are the two most commonly used channels. Events / Professional Learning, Member / Professional Networks & Partnerships, and Website / Online Presence are also frequently used to attract members.

Direct Outreach / Institutional Contacts and Program / Renewal-based Recruitment were also mentioned, but only by a small number of associations.

```{r}
wave_growth <- wave %>%
  mutate(row_number = row_number()) %>%
  select(row_number,`Was that an increase, decrease or stable number?`)

LLM_wave_eve_classified <- LLM_wave_eve_classified %>%
  mutate(row_number = row_number()) %>%
  left_join(wave_growth, by = "row_number")
```

```{r}
target_adv <- LLM_wave_eve_classified %>%
  separate_rows(`Classification - Target Members`,
                sep = "; ") %>%
  separate_rows(`Classification - Member Advertising`,
                sep = "; ")

target_adv_count <- target_adv %>%
  count(
    `Classification - Target Members`,
    `Classification - Member Advertising`
  ) %>%
  group_by(`Classification - Target Members`) %>%
  mutate(
    percentage = n / sum(n) * 100,
    label = paste0(n, "\n(", round(percentage, 1), "%)")
  ) %>%
  ungroup() 
  

target_adv_count %>%
  mutate(`Classification - Target Members` = fct_relevel(`Classification - Target Members`, "Other", after = Inf)) %>%
  ggplot(
  aes(
    x = `Classification - Member Advertising`,
    y = `Classification - Target Members`,
    fill = n
  )
) +
  geom_tile() +
  geom_text(aes(label = label), size = 3) +
  scale_fill_gradient(low = "white", high = "steelblue") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 60, hjust = 1)
  ) +
  labs(
    title = "Advertising Approaches by Target Member Groups",
    x = "Member Advertising",
    y = "Target Members",
    fill = "Count"
  )
```

For Professional Practitioners, Social Media (24.8%) and Email (22.2%) are the two most commonly used recruitment channels. Professional Networks & Partnerships (18.8%) and Professional Learning Events (17.9%) are also important channels, followed by Websites (10.3%). Only a small number of associations use Institutional Contacts (2.6%) or Renewal-based Recruitment (3.4%).

The pattern is similar for Senior Professionals and Early Career members. Social Media and Email are the main channels, while Professional Learning Events and Professional Networks are used as additional recruitment methods.

For Individual Members, associations mainly use a combination of digital channels and professional networks or events. Digital channels provide broad reach, while professional networks and events may provide opportunities for engagement and conversion. Direct one-to-one outreach and renewal-based recruitment are rarely used.

There is also limited differentiation in advertising strategies across different career stages of individual members. Associations tend to use similar channels for Professional Practitioners, Senior Professionals, and Early Career members.

For schools and other organisational target groups, Email (30.8%) and Social Media (23.1%) remain the main recruitment channels, showing a similar overall pattern to individual member recruitment. However, Websites are used more frequently for this group (19.2%). This may indicate that some associations rely more on formal information channels, such as their websites, when communicating with organisations.

Overall, there are some common patterns in recruitment channels across different target groups. Most associations rely on Email and Social Media as core channels, supported by professional networks and event promotion. Although Websites appear to be more important for organisational target groups, there is currently limited evidence of highly differentiated recruitment strategies for different audiences.

# Association–Educators SA Relationship

```{r, eval=FALSE}
# LLM
LLM_wave_rest <- wave %>%
  mutate(serial_num = row_number()) %>%
  select("What kinds of resources/publications do you provide?", "What is your biggest advocacy issue for 2025?", "What are the biggest threats to your Association in 2025?", "What does your Association hope to contribute as an organisation to Educators SA?", "What do you hope to get from being a member of Educators SA?")

write.csv(LLM_wave_rest, "data/LLM_wave_rest.csv")
```

```{r}
LLM_wave_rest_classified <- read_csv("data/LLM_wave_rest_classified.csv")
```

## Advocacy Issues and Organisational Threats

```{r, eval=FALSE}
# LLM

LLM_wave_compare <- wave %>%
  mutate(serial_num = row_number()) %>%
  select("What is your biggest advocacy issue for 2025?", "What are the biggest threats to your Association in 2025?", "What does your Association hope to contribute as an organisation to Educators SA?", "What do you hope to get from being a member of Educators SA?")

write.csv(LLM_wave_compare, "data/LLM_wave_compare.csv")
```

```{r}
LLM_wave_compare_classified <- read_csv("data/LLM_wave_compare_classified.csv")
```

```{r}
# Advocacy Issue Category vs Threats Category
compare_threat <- bind_rows(
  LLM_wave_compare_classified %>%
    separate_rows(`Advocacy Issue Category`, sep = "; ") %>%
    rename(Category = `Advocacy Issue Category`) %>%
    mutate( Type = "Advocacy Issue") %>%
    select(Category, Type),

  LLM_wave_compare_classified %>%
    separate_rows(`Threats Category`, sep = "; ") %>%
    rename(Category = `Threats Category`) %>%
    mutate(Type = "Threats Category") %>%
    select(Category, Type)
) %>%
  count(Category, Type)

compare_threat %>%
  mutate(Category = fct_relevel(Category, "Other", after = Inf)) %>%
  mutate(Category = fct_relevel(Category, "Unsure", after = Inf)) %>%
  ggplot(aes(x = Category, y = n, fill = Type)) +
  geom_col(position = "dodge") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(y = "Count",title = "Advocacy Issue vs Threats Category")
```

For Advocacy Issues, Subject / Program Sustainability & Quality was the most frequently mentioned category, with 12 mentions. This was followed by Access, Equity & Inclusion (9 mentions), Education Policy, Curriculum & Standards (9 mentions), and Workforce & Staffing (8 mentions).

These results show that associations commonly focus their advocacy efforts on issues related to education quality, educational equity, and the education workforce.

For Threat Categories, Membership & Engagement was the most frequently mentioned category, with 15 mentions, followed by Workforce & Staffing (12 mentions). This indicates that associations' main concerns often relate to organisational sustainability, including declining member engagement, member retention, and workforce shortages.

There is a clear difference between the issues associations focus on in their advocacy and the threats they face internally. Advocacy Issues are more focused on education-sector issues, such as Subject / Program Sustainability & Quality, Access, Equity & Inclusion, and Education Policy, Curriculum & Standards. In contrast, the reported threats are more focused on organisational issues, such as Membership & Engagement, Workforce & Staffing, and Organisational Governance & Capacity.

This suggests that while associations seek to contribute to broader developments in education, many of the challenges they face in practice are related to maintaining their membership base and organisational capacity.

Membership & Engagement is the most frequently reported organisational risk. It appeared 15 times in the Threats category but only six times in Advocacy Issues. This indicates that member recruitment, retention, and engagement are common challenges for associations, but they are less frequently identified as issues requiring external advocacy. They may therefore be more commonly treated as internal management and operational issues.

Workforce & Staffing is important in both areas. It appeared eight times in Advocacy Issues and 12 times in Threat Categories. This indicates that workforce-related issues affect both association operations and the wider education sector. This could be an area where associations may have opportunities for cross-association collaboration and joint advocacy.

Overall, associations' advocacy efforts mainly focus on education quality, equity, and policy issues, while their organisational concerns are more focused on member engagement, staffing, and organisational capacity.

## What Associations Can Contribute and What They Expect from Educators SA

```{r}
compare_contribute <- bind_rows(
  LLM_wave_compare_classified %>%
    separate_rows(`Contribution to Educators SA Category`, sep = "; ") %>%
    rename(Category = `Contribution to Educators SA Category`) %>%
    mutate( Type = "Association Can Contribute") %>%
    select(Category, Type),

  LLM_wave_compare_classified %>%
    separate_rows(`Expected Membership Benefits Category`, sep = "; ") %>%
    rename(Category = `Expected Membership Benefits Category`) %>%
    mutate(Type = "Association Wants") %>%
    select(Category, Type)
) %>%
  count(Category, Type)

compare_contribute %>%
  ggplot(aes(x = Category, y = n, fill = Type)) +
  geom_col(position = "dodge") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(y = "Count",title = "What Associations Contribute vs What They Expect from Educators SA")
```

For Association Can Contribute, Specialist Expertise & Perspectives was the most frequently identified category, with 18 mentions. This was followed by Advocacy & Collective Voice (16 mentions), Organisational Support & Capacity (16 mentions), and Networking & Support & Collaboration (14 mentions).

These results indicate that associations commonly see their own role as providing professional knowledge and expertise, contributing to collective advocacy, and supporting organisational development.

For Association Wants, Networking & Support & Collaboration was the most frequently mentioned category, with 31 mentions. This was followed by Information & Knowledge (16 mentions), Governance & Administration (15 mentions), and Advocacy & Collective Voice (13 mentions).

This shows that associations' main expectations of Educators SA are concentrated on networking and collaboration, access to information and knowledge, and governance-related support.

There is a noticeable difference between what associations believe they can contribute and what they expect from Educators SA. Associations place greater emphasis on their own professional expertise and advocacy role, while their expectations are more focused on networking, information, and governance support. This indicates that associations' self-perceived role and their expectations of Educators SA do not fully overlap.

Networking & Support & Collaboration shows the largest difference between the two areas. It was mentioned 31 times under Association Wants but only 14 times under Association Can Contribute, resulting in a difference of 17 mentions. This indicates that collaboration and connection are particularly common areas of expectation, while fewer associations identified this as an area they can contribute to.

Advocacy & Collective Voice and Organisational Support & Capacity are mentioned relatively frequently in both areas. This suggests that associations' existing roles in collective advocacy and organisational support are broadly aligned with the areas where support is also expected.

Overall, associations tend to describe their own role in terms of professional expertise and advocacy, while their expectations of Educators SA are more focused on ongoing networking, collaboration, information, and organisational support. There is relatively strong alignment in advocacy and organisational support, while networking and collaboration show a larger difference between current contribution and expected support.

# Recommendations

## Survey Design

### Improve the Collection of Membership Structure Data

Different types of members should be recorded separately to provide a clearer understanding of membership structure. For example, the survey could ask:

How many Individual Members do you have? How many organisational or school members do you have?

For national organisations, an additional question could ask what proportion of their total national membership is based in South Australia. This would provide a clearer understanding of the size of their South Australian membership.

Instead of asking associations to predict their future membership numbers, the survey could ask for the proportion of members whose membership expired in the previous year and who subsequently renewed. This would provide a more measurable indicator for understanding future membership trends.

### Collect More Information About Geographic Activity

A multiple-choice question could be added to identify the states or cities where associations are most active, for example:

“Which states or cities are your association most active in?”

Some associations did not provide specific location information, resulting in missing data in the current analysis. Collecting this information could provide a better understanding of the geographic distribution of association activities and could also support future collaboration and joint events between associations.

### Simplify the Question About Member Age

The question about member age distribution has a very high level of missing data. This suggests that many associations may not have detailed information about the age structure of their members.

Rather than asking for detailed age distribution, the question could be simplified to something such as:

“Which age group represents the largest proportion of your members?”

A broader question would reduce the reporting burden while still providing useful information about the general age structure of association membership.

### Remove Duplicate Survey Questions

The questions “Do you offer any discounted memberships to Early Career Educators?” and “Do you offer a discounted membership to ‘Early Careers’ or ‘Pre-Service’?” are similar and may collect overlapping information.

The first question could therefore be removed to reduce duplication in the survey.

### Collect Information About Areas of Collaboration

Given the strong demand for collaboration between associations, the survey could ask associations which areas they would be interested in collaborating on, such as Mathematics, Arts, English, or Science.

This information could help Educators SA identify associations with similar interests and organise joint activities or events across multiple associations.

## Data Collection

Where possible, the format of survey responses should be more structured. For example, questions asking for membership numbers could be set to accept numerical values only. Some open-ended questions could also be changed into predefined single-choice or multiple-choice questions.

This would make the data easier to analyse and reduce the effort required from members when completing the survey. It may also reduce unclear responses such as “What do you mean?” or answers that are not directly related to the question.

For questions such as event frequency, predefined ranges could be provided as response options. When an exact number is not essential for the analysis, using ranges may be more appropriate. Some associations were unable to provide exact numbers and instead used approximate descriptions. Using suitable ranges would allow the information to remain useful for analysis while reducing the need for respondents to provide an exact figure.

Structured response options could also improve the level of detail that can be obtained from the data. For example, if Educators SA wants to understand whether an association uses email to communicate with its members directly or through Educators SA, the survey could provide separate options such as “Email” and “Email (through Educators SA)”.

At the same time, predefined response options should include an “Other” option where appropriate, allowing associations to provide information that is not covered by the predefined categories. This can help maintain data completeness while keeping the survey structured.

During the analysis, it was found that Membership Numbers from the old Gateway platform were not transferred to the new WAVE platform. In addition, one association could have multiple Membership Numbers in the Gateway system, potentially because the organisation had registered more than once.

These issues made it more difficult to compare the old and new datasets and merge records correctly. Differences in how association names were entered across the two platforms created additional matching problems.

Instead of relying on association names for data matching, Educators SA could consider assigning each association a permanent unique ID. Although setting up a unique ID system may require some additional work when accounts are first created, it would make future platform migration, data maintenance, and analysis much easier. It would also reduce the time required to manually check and standardise association names.

The current approach of collecting most information at registration does not provide enough information about changes over time, such as changes in membership size.

One possible approach would be to divide the survey into two parts:

- A larger survey at registration: collecting relatively stable information about the association, such as its membership structure, target members, services, and activities.
- A smaller annual renewal survey: collecting information that changes over time, such as current membership numbers, membership changes, event activity, and other annual indicators.

This approach would allow Educators SA to maintain trend data over time while reducing the amount of information associations need to provide each year. It may also reduce the reporting burden for associations and improve the consistency of annual data collection.
